---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

AssociationExplorer2 helps you explore associations between variables with an interactive Shiny interface. This short tutorial covers a typical first workflow.

## 1) Install and launch

```{r eval=FALSE}
install.packages("AssociationExplorer2")
library(AssociationExplorer2)
run_associationexplorer()
```

## 2) Load data

In the app, either:

- upload your own CSV or Excel file, or
- start with the included demonstration data.

For CSV files, use comma separators and dot decimals.

## 3) Choose analysis variables

Select the variables you want to explore and, if needed, a survey-weight variable. The app automatically adapts visualizations to variable types (numeric or categorical).

## 4) Adjust association filters

Use the minimum and maximum association thresholds to focus on weak, moderate, or strong relationships depending on your objective.

## 5) Read the outputs

Use the network view to identify the strongest links, then inspect bivariate plots and summary tables to interpret the relationships in more detail.

## Next step

Open the function reference for full details on launching the app:

- `run_associationexplorer()` in the Reference tab

## For more information

If you would like additional background, you can consult:

- the original AssociationExplorer vignette: <https://github.com/AntoineSoetewey/AssociationExplorer/blob/main/documentation/vignette.md>
- the accompanying published paper: <https://doi.org/10.1016/j.softx.2025.102483>
